### 2018-08-06 paper/intro.tex

Our contributions are as follows: 
\begin{itemize}
  \item We provide the Sphinxes mix-header format which extends 
    Sphinx~\cite{Sphinx} to a source-routed limited random-walk protocol --- 
    \ie each layer of the onion route contains several alternative next nodes.

@@

  \item We use \ac{SPOR} to design \name: a novel, fully decentralized, 
    autonomous and self-organizing file transfer service among users.
\end{itemize}

In the following, in Section~\ref{system-model}, we introduce the
adversary model and the desired privacy properties of \name. Section~\ref{design}
introduces the design of our proposed solution. In Section~\ref{security-discussion}, we lead a security discussion
about advantages and shortcomings of our approach. Section~\ref{Performance}
evaluates \name. 
Finally, Section~\ref{conclusion} discusses future work and conclusions.
% Cashmere: resilient anonymous routing.
% Route fingerprinting in anonymous communications.
% Bridging and fingerprinting:
% Epistemic attacks on route selection
% Breaking the collusion detection mechanism of morphmix
% Denial of service or denial of security? How attacks
% on reliability can compromise anonymity

>>>>

Our contributions are as follows: 
\begin{itemize}
\sonja{commented out my changes, left Daniel's in merge conflict, left
  my changes on paper outline} 
% \item We have designed \name, a novel fully decentralized, autonomous,
% and self-organizing file transfer service among users based on a novel
% concept named Stateless Probabilistic Onion Routes (SPOR), which combines onion routing with
% probabilistic node selection, informed by random peer sampling and
% predictions for node availability;
% \item We have extended Sphinx~\cite{Sphinx}, a compact and secure
%   message header format for mixnets, to allow for sets of nodes
%   instead of single nodes for onion routing layers, resulting in a
%   hybrid between source routing and ad-hoc node  selection that can
%   deal with unreliable nodes;
% \item  We have demonstrated the feasibility of our approach without
%   third-party storage, both in terms of security and performance . Even
%   suboptimal prediction results in successful file transfer with high
%   probability.

  \item We provide the Sphinxes mix-header format which extends 
    Sphinx~\cite{Sphinx} to a source-routed limited random-walk protocol --- 
    \ie each layer of the onion route contains several alternative next nodes.

@@

  \item We use \ac{SPOR} to design \name: a novel, fully decentralized, 
    autonomous and self-organizing file transfer service among users.

\end{itemize}

In the following, in Section~\ref{system-model}, we introduce the
system and adversary models as well as the desired security and privacy properties of \name. Section~\ref{design}
introduces the design of our proposed solution. In
Sections~\ref{security-discussion} and ~\ref{Performance},
respectively, we evaluate the security and performance of our
approach. We set \name into context with related work in
Section~\ref{related-work} and conclude with Section~\ref{conclusion}.

% Cashmere: resilient anonymous routing.
% Route fingerprinting in anonymous communications.
% Bridging and fingerprinting:
% Epistemic attacks on route selection
% Breaking the collusion detection mechanism of morphmix
% Denial of service or denial of security? How attacks
% on reliability can compromise anonymity
